Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\ {\footnotesize \textsuperscript{}}

### 2018-09-03 main.tex
author
dadada

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\
{\footnotesize \textsuperscript{}}}
\author{\IEEEauthorblockN{1\textsuperscript{st} Dafang Zhao}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}}}

\maketitle

\begin{abstract}
  Power generation efficiency of photovoltaic(PV) system is reduced significantly under partial shading or solar cell damage  conditions. This efficiency losses affected by turning on bypass diode of PV panels, which called mismatch losses. Reconfiguration technology to reconfigure electrical series or parallel connection among PV panels can maximize power generation. Recently, an efficient reconfiguration method of PV panel connection to optimize power generation is proposed. The method first list candidate configurations and applies precise power simulations to the candidates. However, some of candidates might not be realized by given PV panels and the paper does not show any systematic way to identify such a feasibility. In this paper, we propose a very fast algorithm to check the feasibility with high accuracy.
%This paper proposes a reconfiguration strategy that finds an optimal configuration among mismatched PV array in a less computational time. This algorithm is very light and suitable for embedded device. The results show that compare with existed reconfiguration method under non-uniform shadow scenario proposed algorithm computes an optimized configuration with less computational time and very high accuracy.
\end{abstract}

@@

Orozco-Gutierrez et al. further proposed a Fast reconfiguration algorithm to optimize power generation by reconfiguring the connection of PV panels \cite{b10}, where the online monitoring \cite{b6} and the power estimation \cite{b7} are utilized. In the method in \cite{b10}, first, close values of fingerprints from monitoring of PV panels are grouped with some representative values, and then possible combinations of reconfiguration are enumerated. Their power values are estimated by \cite{b7} along with careful estimation of possible errors. The method presented a simple feasibility check and obtains estimated power values for all the possible connections for representative values with some error rate \textit{err}, and then select configurations within \textit{err} difference from the largest estimated value as candidates of the optical configurations. 
\begin{table}[htbp]
\caption{DATASET OF PARTIAL-SHADING PV ARRAY}
\begin{center}
\begin{tabular}{cccc}
%\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}None, 22.8, 22.8{]}    \\
P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
\end{tabular}
\label{tab1}
\end{center}
\end{table}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{graphicx}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subfig}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\title{Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\
  {\footnotesize \textsuperscript{}}}

\author{\IEEEauthorblockN{Dafang Zhao, Michiko Inoue, Ooshita Fukuhito}
  \IEEEauthorblockA{\textit{Graduate School of Science and Technology, Nara Institute of Science and Technology (NAIST) \\8916-5 Takoyama-cho, Ikoma, Nara, 630-0192 Japan}}}
%%% \IEEEauthorblock\{dafang-z.yu7, kounoe, f-ooshita\}@is.naist.jp}}
%%% \{dafang-z.yu7, kounoe, f-ooshita\}@is.naist.jp

 \author{\IEEEauthorblockN{Dafang Zhao}
 \IEEEauthorblockA{\textit{Graduate School of Information Science} \\
 \textit{Nara Institute of Science and Technology}}
 \\
 \IEEEauthorblockN{ Michiko Inoue}
 \IEEEauthorblockA{\textit{Graduate School of Science and Technology} \\
 \textit{Nara Institute of Science and Technology}}
 \and
 \IEEEauthorblockN{Fukuhito Ooshita}
 \IEEEauthorblockA{\textit{Graduate School of Science and Technolog} \\
 \textit{Nara Institute of Science and Technology}}}

\maketitle
\begin{abstract}
  Power generation efficiency of photovoltaic(PV) system is reduced significantly under partial shading or solar cell damage  conditions. This efficiency losses affected by turning on bypass diode of PV panels, which called mismatch losses. Reconfiguration technology to reconfigure electrical series or parallel connection among PV panels can maximize power generation. Recently, an efficient reconfiguration method of PV panel connection to optimize power generation is proposed. The method first list candidate configurations and applies precise power simulations to the candidates. However, some of candidates might not be realized by given PV panels and the paper does not show any systematic way to identify such a feasibility. In this paper, we propose a very fast algorithm to check the feasibility with high accuracy.
%This paper proposes a reconfiguration strategy that finds an optimal configuration among mismatched PV array in a less computational time. This algorithm is very light and suitable for embedded device. The results show that compare with existed reconfiguration method under non-uniform shadow scenario proposed algorithm computes an optimized configuration with less computational time and very high accuracy.
\end{abstract}

@@

Orozco-Gutierrez et al. further proposed a Fast reconfiguration algorithm to optimize power generation by reconfiguring the connection of PV panels \cite{b10}, where the online monitoring \cite{b6} and the power estimation \cite{b7} are utilized. In the method in \cite{b10}, first, close values of fingerprints from monitoring of PV panels are grouped with some representative values, and then possible combinations of reconfiguration are enumerated. Their power values are estimated by \cite{b7} along with careful estimation of possible errors. The method presented a simple feasibility check and obtains estimated power values for all the possible connections for representative values with some error rate \textit{err}, and then select configurations within \textit{err} difference from the largest estimated value as candidates of the optical configurations.

The method \cite{b10} needs to check feasibility since their method designate a configuration with number of strings, the number of active modules for one string and current value of each string where the active module means a module whose bypass diode is not working and the number of active modules of strings are common for all the strings have the common control voltage. For example, if a connection requires two strings with two active modules with 3A and 5A for these strings respectively, we might not find possible combination of PV panels. In [10], a simple feasibility check based on the number of active modules for each representative current values. However, we found out that the feasibility check proposed in [10] is optimistic and does not always identify infeasible cases.

%\begin{table}[htbp]
%\caption{DATASET OF PARTIAL-SHADING PV ARRAY}
%\begin{center}
%\begin{tabular}{cccc}
%%\multicolumn{4}{c}{DATASET OF PARTIAL-SHADING PV ARRAY} \\ \hline \hline
%Panels & Vmpp(V)                & Impp (A)            & MPP(W)                 \\ \hline
%P1     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
%P2     & {[}2.9, 17.1, 17.1{]}  & {[}0.5, 3, 3{]}     & {[}1.5, 51.3, 51.3{]}  \\
%P3     & {[}2.9, 2.9, 2.9{]}    & {[}0.5, 0.5, 0.5{]} & {[}1.5, 1.5, 1.5{]}    \\
%P4     & {[}0, 11.4, 11.4{]}    & {[}0, 2, 2{]}       & {[}None, 22.8, 22.8{]}    \\
%P5     & {[}0, 2.9, 11.4{]}     & {[}0, 0.5, 2{]}     & {[}None, 1.5, 22.8{]}     \\
%P6     & {[}2.9, 11.4, 11.4{]}  & {[}0.5, 2, 2{]}     & {[}1.5, 22.8, 22.8{]}  \\
%P7     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]}  \\
%P8     & {[}11.4, 11.4, 11.4{]} & {[}2, 2, 2{]}       & {[}22.8, 22.8, 22.8{]} \\
%P9     & {[}2.9, 11.4, 17.1{]}  & {[}0.5, 2, 3{]}     & {[}1.5, 22.8, 51.3{]} 
%\end{tabular}
%\label{tab1}
%\end{center}
%\end{table}
